---
title: "Store 459"
author: "Training Team"
date: "March 6, 2016"
output: html_document
---

Getting in the Data:

```{r}
path <- "/Users/Patrick/Documents/Meetups/Analyze This/WAND Challange/"
filename <- "Store 459 Predict M1-3 3-2-16.csv"
store459 <- read.csv(paste(path,filename, sep = ""),  na = "*")

#Alternatively you could import the Excel file 
filename <- "Store 459 Predict M1-3 3-2-16.xlsx"

#First you'll need to install the readxl package 
#install.packages("readxl")  

#And load it by typing in this command:
library(readxl)
store459xl <- read_excel(paste(path,filename, sep = ""), sheet = 1, na = "*")
```

Now that we have our data. It's time to clean it up and get it into a form we want. "[tidyr](https://cran.r-project.org/web/packages/tidyr/vignettes/tidy-data.html)" is a good package to tidy up one's data. And "[dyplr](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html)" provides a great set of tools for efficiently manipulating data sets in R. [Here](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf) is a cheat sheet help manipulate data and create variables.
```{r}
#install.packages("tidyr")
#install.packages("dplyr")
library(tidyr)
library(dplyr)
```

Let's look at the data:
```{r}
tbl_df(store459xl)
```
A tbl is like data.frame, but it's shows up in the console much better. You can also use the function "View" with a capital "V" to look at a spreadsheet display. 

Now let's create indicator variables for DOW, Month, Year:
```{r}
store459xl <- cbind(store459xl, model.matrix( ~ Month - 1, data = store459xl))
store459xl <- cbind(store459xl, model.matrix( ~ Year - 1, data = store459xl))
store459xl <- cbind(store459xl, model.matrix( ~ DOW - 1, data = store459xl))
```
This method is a great way of creating indicator variables from a factor variable. 

But if you just need one indicator variable, there are more intuitive methods. 
```{r}
store459xl <- mutate(store459xl, DOW.test = as.numeric(DOW=="Tue"))
```


Now that we've created all of the variables we'll need for analysis, we can begin with our regression modeling. 

```{r}
attach(store459xl)
model1 <- lm(NetSales ~ NewYr + ValDay + Easter + MemDay + Jul4 + Year2014 + MonthJan + MonthFeb + MonthAug + MonthSep + MonthDec + DOWThu + DOWWed + DOWThu + DOWFri + DOWSat + PRCP + Tmax_DegF + `Net$LstYr`)
summary(model1) 
```

Visualizing data:
```{r}
#Create graphs and charts showing how the model fairs against the real data. 
plot.ts(NetSales)

```


