---
title: "GetWeatherInformation"
output: html_document
---

## Setup

We are using the [Rforecastio library](http://rud.is/b/2013/09/08/rforecastio-simple-r-package-to-access-forecast-io-weather-data/) available on [github](https://github.com/hrbrmstr/Rforecastio) in order to interact with the forcast.io api. In order to use the api you will need you api key stored in your `.Renviron` file in you home directory.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(Rforecastio)
```

## Load Location Data

Load our filtered zip code data. These are the locations we are interested in.

```{r Prepare}
filteredZips <- read.csv("~/src/WAND-Challenge/persistant-data/filteredZips.csv")
attributes(filteredZips)
```

For each of the filtered zips we want to request the daily historic weather information from 2013-01-01 to 2015-12-31.

```{r GetWeatherData}
# for (rowNum in 1:length(filteredZips$Zipcode)) {
for (rowNum in 1:2) {
  Zipcode <- filteredZips[rowNum,]$Zipcode
  Lat <- filteredZips[rowNum,]$Lat
  Long <- filteredZips[rowNum,]$Long
  timespan <- seq(ISOdate(2013, 1, 1), ISOdate(2013, 1, 2), by = "day")
  
  for (i in 1:length(timespan)) {
    print(paste("Getting forcast for", Zipcode, "for date", timespan[i], sep = " "))
    fio.list <- get_forecast_for(Lat, Long, format(timespan[i], "%Y-%m-%dT%H:%M:%S"))
    
    if (exists("daily.weather")) {
      rbind(daily.weather, cbind(Zipcode, fio.list$daily))
    } else {
      daily.weather <- cbind(Zipcode, fio.list$daily)
    }
    
    if (exists("hourly.weather")) {
      rbind(hourly.weather, cbind(Zipcode, fio.list$hourly))
    } else {
      hourly.weather <- cbind(Zipcode, fio.list$hourly)
    }
    
  }
  
  write.csv(hourly.weather, "~/src/WAND-Challenge/persistant-data/hourly-weather.csv", row.names = FALSE)
  write.csv(daily.weather, "~/src/WAND-Challenge/persistant-data/daily-weather.csv", row.names = FALSE)
}


```